The Globular Cluster System of the Auriga Simulations

### 2019-01-08 AurigaGCS.tex
Fit ax+b to FeH-Rgc blob, weighted by pass.

\subsection{Harris catalogue}
\label{sec:harris}
\citet[][2010 edition]{1996AJ....112.1487H} provides the most up-to-date and comprehensive catalog of the MW GCS that contains properties of 157 globular clusters. The catalogue is believed to be roughly 90\% complete.

\subsection{Age estimates}
\label{sec:vandenberg}
\citet{2013ApJ...775..134V} measured [Fe/H] and obtained age-estimates for 55 globular clusters in the MW GCS.

@@

\subsection{M31}
\todo[inline]{Get big dataset of M31 GCS}
\label{sec:m31}
\citep{2011AJ....141...61C}
\citep{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}

\section{Results}
\label{sec:results}
\citet{2013ApJ...775..134V} presents age measurements of 55 GCs in the MW. The
mean age of GCs in the MW is $11.9$~Gyr with a dispersion of $0.8$~Gyr. 
Therefore we select all star particles in the Auriga simulations that are older 
than $10$~Gyr. Henceforth we will refer the this subset of star particles as the 
`GC candidates'. Our approach is similar to the one taken by \citep{2017MNRAS.465.3622R},
where we know we are oversampling the real GC population with the contribution
of field stars in our subset. This will be further addressed in the discussion.

@@

>>>>

\subsection{Harris catalogue}
\label{sec:harris}
\citet[][2010 edition, H96]{1996AJ....112.1487H} provides the most up-to-date and comprehensive catalog of the MW GCS that contains properties of 157 globular clusters. The catalogue is believed to be roughly 90\% complete.

\subsection{Age estimates}
\label{sec:vandenberg}
\citet[][V13]{2013ApJ...775..134V} measured [Fe/H] and obtained age-estimates for 55 globular clusters in the MW GCS.

@@

\subsection{M31}
\todo[inline]{Get big dataset of M31 GCS}
\label{sec:m31}
\citep[][C11]{2011AJ....141...61C}
\citep{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}

\section{Results}
\label{sec:results}
\citet{2013ApJ...775..134V} presents observations of 55 GCs in the MW with age-estimates
where the mean value is $11.9\pm0.1$~Gyr with a dispersion of $0.8$~Gyr. Therefore we
investigate the subset of star particles in the Auriga simulations that formed before a
lookback time of $10$~Gyr. Henceforth we will refer the this subset of star particles as
`GC candidates'.

@@

We investigate all star particles in the Auriga simulations that are older than 10~Gyr,
an approach equal to the method of \citep{2017MNRAS.465.3622R}. This approach does not
take the bound cluster fraction \citep[e.g.][]{2012MNRAS.426.3008K} into account. This
means that our sub set, which is based on selection by age, comprises both stars in the
field as well as globular clusters. We compare the total mass in the simulations in 
metallicity ([Fe/H]), galactocentric radius $r_{\text{gc}}$, and [Fe/H]-$r_{\text{gal}}$ 
bins to the total mass in the MW GCS (using the H96 data set). The mass excess in the
simulations gives a maximum mass loss `budget' for the product of cluster formation 
efficiency and dynamical evolution. We find fractions that vary with metallicity,
radius and metallicity-and-radius.

\todo{
``The fraction of all star formation that occurs in bound stellar clusters (the cluster formation efficiency, hereafter CFE) follows by integration of these local clustering and survival properties over the full density spectrum of the ISM, and hence is set by galaxy-scale physics. We derive the CFE as a function of observable galaxy properties, and find that it increases with the gas surface density'' \citep{2012MNRAS.426.3008K}
}

### 2019-01-08 Partial/FeH_logM.tex
Fit ax+b to FeH-Rgc blob, weighted by pass.

    \includegraphics[width=0.49\textwidth]{{MW_M31_Rgc_HistogramMassWeighted}.png}
    \includegraphics[width=0.53\textwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 156 GCs in the MW.
        \emph{Right:} Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass.
        \label{fig:MW-M31-Rgc-FeHRgc}
    }

    \transparent{0.0}\includegraphics[width=0.49\textwidth]
        {{MW_M31_Rgc_HistogramMassWeighted}.png}
    \transparent{1.0}\includegraphics[width=0.53\textwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_VandenBerg2013data}.png}
    \caption{
        Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of
        55 GCs in the Milky Way \citep[data from][]{2013ApJ...775..134V}, which
        is 43.27\% of the total MW GCS mass.
        \label{fig:MW-M31-FeHRgc2}
    }
\end{figure*}
\clearpage
}
\newpage

@@

\afterpage{%
\section{Distribution of Galactocentric radii R$_{\rm GC}$}
\label{sec:FeH}
% \thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit0-trim}.png}
    \caption{
        \scriptsize \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} We use linear regression to obtain log$_{10}$(mass
        normalization) in the domain 0-100 kpc (i.e. we fit $ax+b$ with $a=0$)
        \label{fig:todo1}
    }

@@

\afterpage{%
\label{sec:Rgc}
% \thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-errorbar-trim}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} 
        \label{fig:todo7}
    }

@@

\afterpage{%
\section{Distribution of [Fe/H]-R$_{\rm GC}$}
\label{sec:FeH-Rgc}

@@

    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$-[Fe/H] distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{mean value} 
        (of 40 Auriga haloes)
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        \label{fig:todo2}
    }

@@

\afterpage{%
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_std}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_std}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$-[Fe/H] distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{standard deviation} 
        (of 40 Auriga haloes)
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        \label{fig:todo2}
    }

@@

>>>>

    \includegraphics[width=0.49\textwidth]{{MW_M31_Rgc_HistogramMassWeighted}.png}
    \includegraphics[width=0.53\textwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \caption{
        \emph{Left:} Mass-weighted r$_{\text{gc}}$ distribution of 156 GCs in the MW.
        \emph{Right:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass.
        \label{fig:MW-M31-Rgc-FeHRgc}
    }

    \transparent{0.0}\includegraphics[width=0.49\textwidth]
        {{MW_M31_Rgc_HistogramMassWeighted}.png}
    \transparent{1.0}\includegraphics[width=0.53\textwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_VandenBerg2013data}.png}
    \caption{
        Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of
        55 GCs in the Milky Way \citep[data from][]{2013ApJ...775..134V}, which
        is 43.27\% of the total MW GCS mass.
        \label{fig:MW-M31-FeHRgc2}
    }
\end{figure*}
\clearpage
}
\newpage

@@

\afterpage{%
\section{Distribution of Galactocentric radii r$_{\text{gc}}$}
\label{sec:FeH}
% \thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit0-trim}.png}
    \caption{
        \scriptsize \emph{Left:} Mass-weighted r$_{\text{gc}}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} We use linear regression to obtain log$_{10}$(mass
        normalization) in the domain 0-100 kpc (i.e. we fit $ax+b$ with $a=0$)
        \label{fig:todo1}
    }

@@

\afterpage{%
\label{sec:Rgc}
% \thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-errorbar-trim}.png}
    \caption{
        \emph{Left:} Mass-weighted r$_{\text{gc}}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} 
        \label{fig:todo7}
    }

@@

\afterpage{%
\section{Distribution of [Fe/H]-r$_{\text{gc}}$}
\label{sec:FeH-Rgc}

@@

    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
    \caption{
        \emph{Left:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{mean value} 
        (of 40 Auriga haloes)
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        \label{fig:todo2}
    }

@@

\afterpage{%
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_std}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_std}.png}
    \caption{
        \emph{Left:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{standard deviation} 
        (of 40 Auriga haloes)
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        \label{fig:todo2}
    }

@@

\afterpage{%
\subsection{Distribution of [Fe/H]-r$_{\text{gc}}$: more bins / higher resolution}
\label{sec:FeH-Rgc-4096}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_4096bins_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_4096bins_mean}.png}
    \caption{
        \emph{Left:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{standard deviation} 
        (of 40 Auriga haloes). Difference here is that we `crancked up' the
        resolution, because we can and it's awesome. Note that the range is
        somewhat larger. Observational bin edges are indicated by horizontal and
        vertical lines for convenience.
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        The red line shows a linear fit to the metallicity-radius relation, 
        weighted by mass. The best-fit parameters are indicated in the lower
        left corner.
        \label{fig:todo2}
    }

    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_4096bins_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_4096bins_mean}.png}
    \caption{
        \emph{Left:} Same figure, but for old insitu stars.
        \emph{Right:} Same figure, but for old accreted stars.
        Our linear fit shows the slope of the metallicity profile ($a$), as well
        as the zero crossing point at r$_{\text{gc}}$=1kpc. ($b$). We note that
        the $b$ is $0.49$~dex lower for old star particles than for all star 
        particles. The radial profile of the old \textbf{accreted} star particles
        is 0.18 dex lower than that of the old \textbf{insitu} star particles.
        The gradient $a$ of -0.48 and -0.37 is slightly higher than the findings
        of Harris 1998 Fig.8 p.235, who reports 
        $\Delta$[Fe/H]~/~$\Delta$log~R$_{\text{gc}}$~=~-0.30 for 
        R$_{\text{gc}} \lesssim$~10~kpc.
        \label{fig:todo2}
    }
\end{figure*}
\clearpage
}
\clearpage

\afterpage{%
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_4096bins_std}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_4096bins_std}.png}
    \caption{
        \emph{Left:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{standard deviation} 
        (of 40 Auriga haloes). 
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        \label{fig:todo2}
    }

    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_4096bins_std}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_4096bins_std}.png}
    \caption{
        \emph{Left:} Same figure, but for old insitu stars.
        \emph{Right:} Same figure, but for old accreted stars.
        \label{fig:todo2}
    }
\end{figure*}
\clearpage
}
\clearpage

\section{Properties of birth haloes of the accreted population}
\label{sec:accreted-birth-haloes}
